---
title: "P8105 Homework 1"
author: "Laylah Jones"
date: 2023-09-21
output: github_document
---

```{r}
library(tidyverse)

library(moderndive)
```

# Problem 1

```{r}
# Accessing dataset information

data("early_january_weather")
nrow(early_january_weather)
ncol(early_january_weather)
```


```{r}
# Finding the mean

mean(pull(early_january_weather, temp))
```


The structure of the dataset is looking at the meteorological weather during early January. The 15 variables included are origin, year, month, day, hour, temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, pressure, visibility, and the time hour. The values of important values are the ones that are dependent and changing in the dataset such as temp, dewp, humid, wind_dir, wind_speed, wind_gust, and pressure. However, the important value that we are focusing on now is the temperature. The dataset has 358 rows and 15 columns. The mean is 39.58212. 

```{r}
# Making a scatter plot

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

The apparent pattern is that as the time increases the temperature fluctuates. As time goes on, the humidity and temperature have a general increase. 

```{r}
ggsave("early_january_weather.pdf")
```


# Problem 2

```{r}
# This code chunk creates a data frame 

hw_df = 
  tibble(
    vec_numeric = rnorm(10),
    vec_char = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
    vec_factor = factor(c("High", "High", "Low", "Medium", "Medium", "Low", "High", "Low", "Low", "Low")),
    vec_logic = vec_numeric > 0
  )
hw_df
```

