---
title: "P8105 Homework 1"
author: "Laylah Jones"
date: 2023-09-22
output: github_document
---

```{r}
library(tidyverse)

library(moderndive)
```

# Problem 1

```{r}
# Accessing dataset information.

data("early_january_weather")
nrow(early_january_weather)
ncol(early_january_weather)
```


```{r}
# Finding the mean.

mean(pull(early_january_weather, temp))
mean(pull(early_january_weather, humid))
```


The structure of the dataset is looking at the meteorological weather during early January. The 15 variables included are origin, year, month, day, hour, temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, pressure, visibility, and the time hour. The dataset has 358 rows and 15 columns. The values of important values are the ones that are dependent and changing in the dataset such as temp, dewp, humid, wind_dir, wind_speed, wind_gust, and pressure. However, the important value that we are focusing on now is the temperature and humidity. The mean temperature 39.58212 or around 40 degrees. The mean humidity is 65.4767 or around 65. 

```{r}
# Making a scatter plot.

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

The apparent pattern is that as the time increases the temperature fluctuates. As time goes on, the humidity and temperature have a general increase. 

```{r}
ggsave("early_january_weather.pdf")
```


# Problem 2

```{r}
# Creating a data frame. 

hw_df = 
  tibble(
    vec_numeric = rnorm(10),
    vec_char = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
    vec_factor = factor(c("High", "High", "Low", "Medium", "Medium", "Low", "High", "Low", "Low", "Low")),
    vec_logic = vec_numeric > 0
  )
hw_df

# Now I will find the mean of each variable in the dataframe.

mean(pull(hw_df, vec_numeric))
```


```{r}
# This code chunk applies the as.numeric function to the logical, character, and factor variables.

as.numeric(pull(hw_df, vec_char))
as.numeric(pull(hw_df, vec_factor))
as.numeric(pull(hw_df, vec_logic))

eval = FALSE
```

When I ran the as.numeric function, it converted the logical, character, and factor variables into numeric variables. It does this to make my data frame variables more interpretable as numbers instead of as phrases. This helps explains what happens when I try to get the mean because you cannot get the mean of variables from phrases, however by turning the phrases into numerical variables you can then use the formula of mean. For example, the mean of the factor variables (which were in the form of High, Medium, and Low) were converted so that each variable is represented numerically (High = 1, Medium = 3, Low = 3), you can take the sum of those numbers which is 19, and divide it by the number of variables in the data frame which is 10 to get a mean of 1.9. 
